---
title: "HW4"
author: "Weijian Cai"
date: "March 3, 2019"
output: html_document
---
load the required library
```{r}
library(readr)
library(tidyr)
library(dplyr)
```

load csv file into R
```{R}
raw<- read.csv("https://raw.githubusercontent.com/Weicaidata/607/master/airline%20database.csv")
str(raw)
raw
```

use tidyr to pivot table from wide to long table for further analysis
```{r}
df_gather <- gather(raw,city,flightnum,Los.Angeles:Seattle)
df_gather
```

use spread functon to add delayed and 'on time' columns
```{r}
df_spread <- spread(df_gather,Status,flightnum)
df_spread
```

use dpylr to add another two column ontime percentage and delayed percentage.
```{r}
df <- df_spread %>% 
  mutate(total= delayed +df_spread$`on time`,ontime_perc=`on time`/total,delayed_perc=delayed/total)
df
```


use bar to compare the ontime percentage between two lines, find that they are very similar, not much differnt.
```{r}
library(ggplot2)
ggplot(df, aes(x = Airline, y=ontime_perc, fill = city)) +
    geom_bar(stat="identity",position="dodge") + 
    xlab("Airline") + ylab("ontime_perc") 

```

however, the delayed percentage between two airlines, we can see that ALaska airline of each lines are lower than AM WEST, it mean ALASKA is doing better than AM WEST.
```{r}

ggplot(df, aes(x = Airline, y=delayed_perc, fill = city)) +
    geom_bar(stat="identity",position="dodge") + 
    xlab("Airline") + ylab("delayed_perc") 
```

