---
title: "Assignment3_607"
author: "Weijian Cai"
date: "February 16, 2019"
output: html_document
---

###Problem 3
####(A)
load the raw data into R
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
raw.data
```

we use stringr library for data manipulation
```{r}
library(stringr)
```

looking for alphabetic characters, also contain period,commas and empty spaces, and add a quantifier that at least length two.
```{r}
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```

####(B)

find any character text from 2 to 3 character follow by "."
```{R}
title<-str_detect(name,"[\\w]{2,3}\\. ")
cbind(name,title)
```

####(C)
```{r}
sec_name = str_detect(name,"\\s[A-z]\\. ")
cbind(name,sec_name)
```

###Question 4
####(A)[0-9]+\\$
One or more digit numbber and follow by "$"sign

```{r}
sample1 = 'abc123$123'
a<-str_extract_all(sample1,'[0-9]+\\$')
a
```

####(B)\\b[a-z]{1,4}\\b
word edge and charater letter with length 1 to 4 and word edge

```{r}
example2 = 'abcde abc'
str_extract_all(example2,"\\b[a-z]{1,4}\\b")
```


####(C).*?\\.txt$
Start with any character,  * means zero or more time, ? means optional or one times, a period,txt at the end.

```{r}
example3 ='.local.txt'
str_extract_all(example3,".*?\\.txt$")
```


####(D)\\d{2}/\\d{2}/\\d{4}
Any digital with length2/any digital with length 2/ any digital with length of 4.
```{r}
example4= '02/17/2019'
str_extract_all(example4,"\\d{2}/\\d{2}/\\d{4}")
```

####(E)<(.+?)>.+?</\\1>
'<any character> any character </contents of group 1>'
```{r}
example5 = '<any>anything</any>'
str_extract_all(example5,"<(.+?)>.+?</\\1>")
```

