---
title: "Week2_HW_607"
author: "Weijian Cai"
date: "February 9, 2019"
output: html_document
---
### Create talbe movies,respondents,survey in movie_survey database.And populate data into tables.
CREATE TABLE `movie_survey`.`movies` (
  `movies_id` INT NOT NULL,
  `moviesname` VARCHAR(45) NULL,
  `type` VARCHAR(45) NULL,
  PRIMARY KEY (`movies_id`));
  
INSERT INTO `movie_survey`.`movies` (`movies_id`, `moviesname`, `type`) VALUES ('1', 'The Lego Movie 2', 'animation');
INSERT INTO `movie_survey`.`movies` (`movies_id`, `moviesname`, `type`) VALUES ('2', 'What Men Want', 'comedy');
INSERT INTO `movie_survey`.`movies` (`movies_id`, `moviesname`, `type`) VALUES ('3', 'Cold Pursuit', 'action');
INSERT INTO `movie_survey`.`movies` (`movies_id`, `moviesname`, `type`) VALUES ('4', 'The Final Wish', 'horror');
INSERT INTO `movie_survey`.`movies` (`movies_id`, `moviesname`, `type`) VALUES ('5', 'Glass', 'drama');
INSERT INTO `movie_survey`.`movies` (`movies_id`, `moviesname`, `type`) VALUES ('6', 'The Upside', 'Comedy');


CREATE TABLE `movie_survey`.`respondents` (
  `respondents_id` INT NOT NULL,
  `firstname` VARCHAR(45) NULL,
  `lastname` VARCHAR(45) NULL,
  `sex` VARCHAR(45) NULL,
  PRIMARY KEY (`respondents_id`));
  
 
INSERT INTO `movie_survey`.`respondents` (`respondents_id`, `firstname`, `lastname`, `sex`) VALUES ('1', 'jacky', 'jordon', 'm');
INSERT INTO `movie_survey`.`respondents` (`respondents_id`, `firstname`, `lastname`, `sex`) VALUES ('2', 'tom', 'peter', 'm');
INSERT INTO `movie_survey`.`respondents` (`respondents_id`, `firstname`, `lastname`, `sex`) VALUES ('3', 'rose', 'white', 'f');
INSERT INTO `movie_survey`.`respondents` (`respondents_id`, `firstname`, `lastname`, `sex`) VALUES ('4', 'susan', 'lu', 'f');
INSERT INTO `movie_survey`.`respondents` (`respondents_id`, `firstname`, `lastname`, `sex`) VALUES ('5', 'ken', 'harroon', 'm');

CREATE TABLE `movie_survey`.`survey` (
  `survey_id` INT NOT NULL,
  `respondent_id` INT NULL,
  `movie_id` INT NULL,
  `score` INT NULL,
  `date` DATE NULL,
  PRIMARY KEY (`survey_id`));

INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('1', '1', '2', '5', '2019-02-09');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('3', '1', '1', '4', '2019-02-09');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('2', '1', '3', '3', '2019-02-09');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('4', '1', '4', '4', '2019-02-09');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('5', '1', '5', '5', '2019-02-09');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('6', '2', '1', '5', '2019-02-08');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('7', '2', '2', '4', '2019-02-08');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('8', '2', '3', '4', '2019-02-08');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_  id`, `movie_id`, `score`, `date`) VALUES ('9', '2', '4', '1', '2019-02-08');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('10', '2', '5', '5', '2019-02-08');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('11', '3', '1', '4', '2019-02-07');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('12', '3', '2', '5', '2019-02-07');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('13', '3', '3', '4', '2019-02-07');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('14', '3', '4', '5', '2019-02-07');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('15', '3', '5', '3', '2019-02-07');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('16', '4', '1', '5', '2019-02-06');  
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('17', '4', '2', '3', '2019-02-6');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('18', '4', '4', '5', '2019-02-06');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('19', '4', '5', '3', '2019-02-06');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('20', '4', '3', '5', '2019-02-06');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('21', '5', '1', '3', '2019-02-05');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('22', '5', '2', '5', '2019-02-05');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('23', '5', '3', '4', '2019-02-05');
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('24', '5', '4', '5', '2019-02-05');    
INSERT INTO `movie_survey`.`survey` (`survey_id`, `respondent_id`, `movie_id`, `score`, `date`) VALUES ('25', '5', '5', '4', '2019-02-05');  

```{r}
library(RMySQL)
library(DBI)
library(dplyr)
```
### connect mysql database through R
```{r}
mydb <-dbConnect(MySQL(), user='wei', password='0000', dbname='movie_survey', host='localhost')
```

###write sql to join three tables
```{R}
sr<- dbGetQuery(mydb, "
                select s.survey_id, r.firstname, r.lastname, r.sex,                                   m.moviesname, m.type, s.score,s.date
                from survey s
                     join movies m on s.movie_id = m.movies_id
                     join respondents r on s.respondent_id = r.respondents_id")
head(sr)
```


###create a subset sub_sr
```{r}
sub_sr<-sr%>%select(moviesname,score)

head(sub_sr,n=10)
```

###calculate the average of score.  
```{r}
sub_sr %>%
  group_by(moviesname) %>%
  summarise(avg_score = mean(score))
```








