---
title: "Project2"
author: "Weijian Cai"
date: "March 9, 2019"
output: html_document
---
##Dataset:Zillow data on 2018 Median Rental Price/sqft by State by Sunny Mehta

load the required library to tidy and modify data for further analysis
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
```

load csv dataset by into R
```{r}
url <- "https://raw.githubusercontent.com/Weicaidata/607/master/State_MedianRentalPricePerSqft_AllHomes.csv"
df1 <- read.csv(url,header=TRUE)
head(df1)
```

rename the columns for better understanding the data
```{r}
colnames(df1) <- c("state","size","aJan","bFeb","cMar","dApr","eMay","fJun","gJul","hAug","iSep","jOct","kNov","lDec")
head(df1)
```

use glimpse function in dplyr to examine the dataset, and use summary function to see if there is missing value
```{r}
glimpse(df1)
summary(df1)

```

use gather function from tidyr to make the wide dataset into long, and sort by "size"
```{r}
df2 <- gather(df1,"month","sales",3:14) %>% 
  arrange(size)
head(df2)
```


##answer question "overall current distribution"
we can use histgram to see that it is a right skewed distributed, and use summary function to find out the mean, min,max,1st quartille and 3rd quartille.
```{r}
hist(df2$sales,main="sales",xlab="Averge")
summary(df2$sales)
```

##answer question "sales trend by months"
use summarise funtion group by"month"
```{r}
df3 <- df2 %>% 
  arrange(month) %>% 
  group_by(month) %>% 
  summarise(avg=mean(sales))
df3
```

from the graph below, we can see that summer is hot season for sales of house, winter is the low season, which is within our expectation.
```{r}
ggplot(data=df3,aes(x=month,y=avg,group=1))+
  geom_line()+
  geom_point()+
  xlab("Month")+
  ylab("Total")+
  labs(title="Sales trend by month")
```


##answer question" trend by states"
we want to see top 5 largest state's sales over year.
```{r}
df6 <- df2 %>% 
  filter(size<=5)
head(df6)
```

NY has the hightst sales price per sqf compare to other states, buth the price for other states are more steady.
```{r}
ggplot(df6,aes(x=month,y=sales,color=state,group=state))+
   geom_line() +
  xlab('Month')+labs(title = "Top 5 states sales trend")
```


