---
title: "Week13 Assignemnt-NoSQL Migration"
author: "Weijian Cai"
date: "April 29, 2019"
output: html_document
---

For this assignment,take information from a relational database and migrate it to a NoSQL database.

```{r}
library(RMySQL)
library(sqldf)
library(mongolite)
```

###Connect to local MySQL Database
```{r}
mydb<-dbConnect(MySQL(), user='wei', password='0000', dbname='movie_survey', host='localhost')
```

###write sql to join three tables
```{r}
sr<- dbGetQuery(mydb, "
                select s.survey_id, r.firstname, r.lastname, r.sex,                                   m.moviesname, m.type, s.score,s.date
                from survey s
                     join movies m on s.movie_id = m.movies_id
                     join respondents r on s.respondent_id = r.respondents_id")
head(sr)
```

###Disconnect from local mysql database
```{r}
dbDisconnect(mydb)
```

###migrate database into local Mongodb database
```
mangodb <- mongo(collection = "airports", db = "mgdb")
```



####Advantage of relational database
It works with well-structured data. We can easily pull data from database like MySQL writing SQL. 

###Advantage of NoSQL database
A NoSQL database is good for storing and processing large amounts of unstructured data.

####Disadvantages of relational databases
1.It requires well developed architecture before loading data into database, it could be huge challenge when we deal with a large and complicate dataset. 
2.It requires someone who has great expertise to design the database to fulfill the 3 normalization forms.
It is time consuming for optimizing the database which is very complicated.

####Disadvantages of NoSQL databases
It lacks of standardization, it may needs a standard query language like SQL.
